%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{carl-philipp }{harmant}{software engineer}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------


\begin{aside} % In the aside, each new line forces a line break
\section{about}
{\color{darkgray}Chicago, Illinois
USA
~
+1 (312) 834 1637
~
\email{cp.harmant@gmail.com}
\linkedin{carlphilipp}
\github{carlphilipp}
\section{languages}
english (fluent)
french (native)
\section{programming}
%{color{red} $\varheartsuit$} Java
%{\color{red} $\varheartsuit$} Android
Java, Android
C\#, \LaTeX
JavaScript, SQL
HTML, CSS, PHP
\section{frameworks}
Spring, Camel
RxJava, OSGi 
Play Framework
\section{tools}
Maven, Gradle, Git
JIRA, Bamboo
GitHub
\section{databases}
Oracle, MySQL
MongoDB}
\section{servers}
Tomcat, Karaf 
Apache, JBoss
\section{os}
GNU/Linux, OSX
Windows
%\section{interests}
%Running
%Basketball
%Volleyball
%Travels
\end{aside}

\section{personal synopsis}

Currently working as a software engineer, I am interested in exploring new challenges. I am passionate about developing, configuring and testing software. My preferred programming language is Java, however I am open to learning about or utilizing any programming language. In my free time, I enjoy working on my Android application "Chicago Commutes", a Chicago public transit tracker, as well as publishing some of my source code on GitHub. I'm also a member of the Chicago Java User group.


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}


\begin{entrylist}

\entry
{2015--Present}
{1 year 6 months}
{Senior Software Engineer} 
{Peapod Propulsion Labs}
{Chicago, Illinois, Unites States}
{Member of the Web Center team, in charge of developing and maintaining several public websites. Some of my daily responsibilities include:\\
\vspace{-4mm}
\begin{itemize}
	\item Collaborating with product owners, business analysts and other team members in a cross-functional Agile environment to produce a content management system that is fully integrated with various loyalty, coupon, and user account systems.
		\item Developing a Spring MVC proxy application around our ESB to allow OAuth2 protected REST APIs to be used by our websites.
	\item Developing a modular REST-driven integration API using Apache Camel, Karaf, ActiveMQ and various other libraries.
	\item Designing and implementing new features using TDD (Test Driven Development).
	\item Improving software quality, reusability, extensibility and consistency.
	\item Verifying and validating features via unit testing, integration testing and automated acceptance testing (Serenity BDD).
	\item Participating in support rotation and troubleshooting production issues to ensure the continued operations of the business.
	\item Main technologies used : Java, Spring, Apache Camel, OSGi, OAuth2, ActiveMQ.
\end{itemize}
}
\vspace{-7mm}

\end{entrylist}

%------------------------------------------------

\begin{entrylist}

\entry
{2012--2015}
{3 years 1 month}
{Software Consultant} 
{Pros}
{Chicago, Illinois, Unites States}
{I was part of the Professional Services team providing expertise to customers related to the
Configure/Price/Quote (CPQ) solutions and more specifically involved in the following activities:\\

\vspace{-4mm}
\begin{itemize}
	\item Integrating Pros CPQ solutions in the IT landscape by using web services.
	\item Interfacing Pros CPQ solutions for data loading purposes.
	\item Development of additional Java EE plugins to fit specific customer needs.
    \item Designing the User Interface (HTML based xml files, CSS, Javascript).
    \item Java-based macrolanguage developing and use of built-in configuration tools.
    \item Responsible for deploying in our Cloud environment.
    %\item Issue management/resolution in a SaaS environment.
    \item Main technologies used : Java, JavaScript, HTML, CSS, Salesforce.com (Apex, Force.com), Oracle, JBoss, JSON, XML, SOAP.
\end{itemize}}
\vspace{-7mm}

\end{entrylist}

%------------------------------------------------

\begin{entrylist}

\entry
{2011}
{6 months}
{Java EE Developer} 
{Fujitsu Technology Solutions}
{Luxembourg City, Luxembourg}
{Arquillian is a tool, made by JBoss, which allows developers to test the components of their
application in a container:\\

\vspace{-4mm}
\begin{itemize}
	\item Made a solution to improve the way to use Arquillian.
	\item Improved the company test process by the creation of a Maven plugin which generates an Arquillian test class.
	\item Automated search of dependencies needed for the archive deployed on the server.
    \item Utilized Maven, JUnit, EJBs, Cobertura, and many other tools and frameworks.
\end{itemize}}
\vspace{-7mm}

\end{entrylist}

%------------------------------------------------

\begin{entrylist}

\entry
{2010}
{5 months}
{Analyst Programmer} 
{Sailendra}
{Nancy, France}
{Sailendra created a technology of user profiling. That technology creates a profile of each user and predicts their comportments based on their actions and artificial intelligence algorithms.\\

\vspace{-4mm}
\begin{itemize}
	\item Managed a project from initiation to implementation overseeing the planning, functional specifications, technical specifications, development and testing.
	\item Worked with the client to ascertain and identify their specific requirements.
	\item Automated search of dependencies needed for the archive deployed on the server.
   \item Created a Firefox plugin for Salendra technology and learnt new technologies like XUL, Spring, Zope/Plone, DTML or Python.
\end{itemize}}
\vspace{-7mm}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{personnal projects}

\begin{entrylist}

\entry
{2014--2017}
{}
{Chicago Commutes}
{  Android Application}
{}
{Android application that helps commuting in Chicago. CTA (trains/buses) \& Divvy (bikes).\\
Technology used : Android SDK, XML, JSON, Google APIs, RxJava, Realm.\\
\footnotesize{Source: \href{https://github.com/carlphilipp/chicago-commutes}{https://github.com/carlphilipp/chicago-commutes}}\\
\footnotesize{Download: \href{https://play.google.com/store/apps/details?id=fr.cph.chicago}{https://play.google.com/store/apps/details?id=fr.cph.chicago}}}

\end{entrylist}

\begin{entrylist}

\entry
{2013--2017}
{}
{Stock Tracker}
{  Website \& Android Application}
{}
{Website and Android application that helps following your stock performance.\\
Technology used: Java, Android SDK, JSON, YQL (Yahoo Query Language), JSP, JSTL, MyBatis,
JUnit, Ant, Cobertura, PMD, Checkstyle, Quartz, JQuery, flotr2, Jasper, Dropbox API, JavaMail,
MySQL, Tomcat.\\
\footnotesize{Sources: \href{https://github.com/carlphilipp/stock-tracker}{https://github.com/carlphilipp/stock-tracker} \& \href{https://github.com/carlphilipp/stock-tracker}{https://github.com/carlphilipp/stock-tracker-android}}}

\end{entrylist}

\begin{entrylist}

\entry
{2014--2016}
{}
{Be My Chef}
{  RESTful API}
{}
{Java-based RESTful API with JSON output.\\
Technology used : Java, Maven, Spring Boot, Jackson, JSON, JUnit, Mockito, Stripe, Mandrill, GeoJSON, Quartz, Findbugs, Jacoco, PMD, MongoDB, JIRA, Git.\\
\footnotesize{Source: \href{https://github.com/carlphilipp/be-my-chef}{https://github.com/carlphilipp/be-my-chef}}
}

\end{entrylist}


\begin{entrylist}

\entry
{2009--2012}
{}
{Management tool for Hyperiums.com}
{Website}
{}
{Alliance management tool to help players gather and analyze data.\\
Technology used : Java, JSP, JSTL, JQuery, iBATIS, PHP, Wamp, MySQL, Tomcat.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2013}
{}
{Masters {\normalfont of Software Engineering}}
{}
{Exia.Cesi, Nancy, France}
{}

%------------------------------------------------

\entry
{2011}
{}
{Bachelors {\normalfont of Software Engineering}}
{}
{Exia.Cesi, Nancy, France}
{}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

\section{certifications}

\begin{entrylist}

%------------------------------------------------

\entry
{2015}
{}
{MongoDB for Java Developers}
{MongoDB University}
{}
{}

\entry
{2013}
{}
{MongoDB for Node.js Developers}
{MongoDB University}
{}
{}

\entry
{2011}
{}
{OCJP : Oracle Certified Java SE 6 Programmer}
{Oracle}
{}
{}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{interests}

%In my spare time, I enjoy running, biking and playing basketball. I ran two marathons in Chicago. I also enjoy reading about and working with new technology, both software and hardware products. I love to travel and explore foreign countries to experience different languages, lifestyles and cultures.

\end{document}